\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Martin Medina} \\ \vspace{1pt}
    \small +1 (438)835-6948 $|$ \href{mailto:medinammartin3@gmail.com}{\underline{medinammartin3@gmail.com}} $|$
    \href{https://github.com/medinammartin3}{\underline{github.com/medinammartin3}} $|$ 
    \href{https://medinammartin3.github.io/}{\underline{medinammartin3.github.io}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Montreal}{Montreal, Canada}
      {Bachelor's Degree in Computer Science}{Sep. 2022 -- Apr. 2025 (expected)}
    \resumeSubheading
      {Lycée Français Louis Pasteur}{Bogota, Colombia}
      {High School | Excellence Award}{2015 -- 2018}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Teaching Assistant}{September 2023 -- April 2024}
      {University of Montreal}{Montreal, Canada}
      \resumeItemListStart
        \resumeItem{Courses: 
            \resumeItemListStart 
                \resumeItem{IFT 1005 - Web Design and Development $|$ (\textit{Sep. 2023 -- Dec. 2023})}
                \resumeItem{IFT 1144 - Introduction to Internet Programming $|$ (\textit{Sep. 2023 -- Apr. 2024})}
                \resumeItem{IFT 1990 - Computing for Social Sciences $|$ (\textit{Jan. 2024 -- Apr. 2024})}
            \resumeItemListEnd
        }
        \hspace{0.5cm}
        \resumeItem{Answering student questions, grading assignments, preparing practical exercises, and supplementing professors' explanations with use cases.}
        \resumeItem{Positive feedback from students indicating that explanations and exercises helped understand the course material and, consequently, improve their results. Very positive feedback from professors, leading to multiple rehires.}
      \resumeItemListEnd

    \resumeSubheading
      {Summer School Counselor}{July 2024}
      {University of Montreal}{Montreal, Canada}
      \resumeItemListStart
        \resumeItem{Planning, organizing, and leading activities focused on fun and teamwork.}
        \resumeItem{Ensuring the safety of the summer school environment and responding to emergencies.}
        \resumeItem{Promoting a sense of inclusion and belonging among participants.}
        \resumeItemListEnd

    \resumeSubheading
      {Python Workshop Leader -- Summer School}{July 2024}
      {University of Montreal}{Montreal, Canada}
      \resumeItemListStart
        \resumeItem{Introducing participants to computing by teaching the basics of Python programming and digital tools.}
        \resumeItem{Designed interactive and engaging lessons to develop their interest and computing skills. The goal was to provide an introduction to computing to guide their choice of field of study at university.}
        \resumeItem{Created the "Hangman" game in Python.}
      \resumeItemListEnd

    \resumeSubheading
      {Team Leader}{September 2022 -- May 2024}
      {Tim Hortons}{Montreal, Canada}
      \resumeItemListStart
        \resumeItem{Customer service, staff training, quality control, and inventory and banking deposit management.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Programming Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, HTML/CSS, JavaScript, Java, SQL (PostgreSQL), C/C++, Haskell, LaTeX} \\
     \textbf{Libraries and Frameworks}{: Django, Numpy, JQuery, AJAX, JUnit, Maven, JavaFX, Jakarta Persistence API} \\
     \textbf{Tools}{: Git, VS Code, PyCharm, IntelliJ, CLion} \\
     \textbf{Others}{: Data structures, Algorithms, Databases, UML, Bash}
    }}
 \end{itemize}


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{Survey Web Application} $|$ \emph{Python, Django, HTML/CSS, JavaScript}}{In development}
          \resumeItemListStart
            \resumeItem{Online survey web application developed with Django that allows users to create surveys, vote on existing surveys, view survey results, and share their surveys.}
            \resumeItem{Using Django for its built-in features for managing user authentication and data storage, and for promoting efficient development.}
            \resumeItem{\textbf{GitHub Repository}: \href{https://github.com/medinammartin3/Sondi}{\underline{github.com/medinammartin3/Sondi}}}
          \resumeItemListEnd

          \resumeProjectHeading
          {\textbf{Online Shopping Website} $|$ \emph{HTML/CSS, JavaScript, JQuery, AJAX}}{Fall 2022}
          \resumeItemListStart
            \resumeItem{Implementation of the front-end of an interactive online shopping website.}
            \resumeItem{Using AJAX to dynamically update and display product information on the website, improving the user experience by reducing page reloads and providing real-time data.}
            \resumeItem{\textbf{Link to Website}: \href{https://medinammartin3.github.io/OnlineShop/index.html}{\underline{https://medinammartin3.github.io/OnlineShop/index.html}}}
            \resumeItem{\textbf{GitHub Repository}: \href{https://github.com/medinammartin3/TP3_IFT1005}{\underline{https://github.com/medinammartin3/TP3\_IFT1005}}}
          \resumeItemListEnd

          \resumeProjectHeading
          {\textbf{Unishop} $|$ \emph{Java, JUnit, Maven}}{Fall 2023}
          \resumeItemListStart
            \resumeItem{Online store simulation program with a command-line interface. Implements a file-based database and includes many features for buyers and sellers.}
            \resumeItem{Managing accounts for sellers and buyers. All information such as completed orders and products for sale are recorded and preserved for each user.}
            \resumeItem{Using JUnit for unit testing to avoid bugs caused by new updates.}
            \resumeItem{\textbf{GitHub Repository}: \href{https://github.com/medinammartin3/Projet_IFT2255}{\underline{github.com/medinammartin3/Projet\_IFT2255}}}
          \resumeItemListEnd

          \resumeProjectHeading
          {\textbf{Course Registration Application for Students} $|$ \emph{Java, JavaFX, Maven}}{Winter 2023}
          \resumeItemListStart
            \resumeItem{Client-server application allowing users (students) to register for courses with a graphical interface implemented with JavaFX.}
            \resumeItem{Recording choices in a simple text-based database.}
            \resumeItem{Using JavaFX for the graphical interface.}
            \resumeItem{\textbf{GitHub Repository}: \href{https://github.com/medinammartin3/Inscriptions_UdeM}{\underline{github.com/medinammartin3/Inscriptions\_UdeM}}}
            \resumeItem{\textbf{Demo Video}: \href{https://youtu.be/T4D-IG02jn4?si=T_W0DgzJoF3X0ABN}{\underline{https://youtu.be/T4D-IG02jn4?si=T\_W0DgzJoF3X0ABN}}}
          \resumeItemListEnd

          \resumeProjectHeading
          {\textbf{Personal Website} $|$ \emph{HTML/CSS, JavaScript}}{}
          \resumeItemListStart
            \resumeItem{Website for my CV and Portfolio}
            \resumeItem{\textbf{Link to Website}: \href{https://medinammartin3.github.io}{\underline{https://medinammartin3.github.io}}}
            \resumeItem{\textbf{GitHub Repository}: \href{https://github.com/medinammartin3/medinammartin3.github.io}{\underline{github.com/medinammartin3/medinammartin3.github.io}}}
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd



 %-----------LANGUAGES-----------
\section{Languages}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{French}{: 100\% (spoken and written)} \\
     \textbf{English}{: 80\% (spoken and written)} \\
     \textbf{Spanish}{: 100\% (spoken and written)} \\
     \textbf{Portuguese}{: 60\% (spoken and written)}
    }}
 \end{itemize}


%-----------REFERENCES-----------
\section{References}
 \begin{itemize}[leftmargin=0.15in, label={}]
     \resumeSubheading
         {Souhila Benbetka}{}{Professor -- University of Montreal}{}
         \resumeItemListStart
             \resumeItem{\textbf{Email}: \href{mailto:souhila.benbetka@umontreal.ca}{\underline{souhila.benbetka@umontreal.ca}}}
         \resumeItemListEnd
         
     \resumeSubheading
         {Abdelhakim Senhaji Hafid}{}{Professor -- University of Montreal}{}
         \resumeItemListStart
             \resumeItem{\textbf{Email}: \href{mailto:ahafid@iro.umontreal.ca}{\underline{ahafid@iro.umontreal.ca}}}
         \resumeItemListEnd
         
     \resumeSubheading
         {Nesrine Mohamed Said}{}{Summer School Coordinator -- University of Montreal}{}
         \resumeItemListStart
             \resumeItem{\textbf{Email}: \href{mailto:nesrine.mohamed.said@umontreal.ca}{\underline{nesrine.mohamed.said@umontreal.ca}}}
         \resumeItemListEnd
 \end{itemize}



%-------------------------------------------
\end{document}
